Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2019-11-04 manuscript/climate_sensitivity_SI.Rmd
Updated caption to reflect Table S5
created and added Fig. S2- drought plot

kable(tableS5, booktabs=TRUE, format = "latex", caption = "Table S4. Correlation of species' traits with tree height across all individuals in the ForestGEO plot") %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE, latex_options = "hold_position")
```

@@

>>>>

kable(tableS5, booktabs=TRUE, format = "latex", caption = "Table S5. Correlation of species' traits with tree height across all individuals in the ForestGEO plot") %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE, latex_options = "hold_position")
```

@@

\newpage
![Figure S2: Time series of Palmer Drought Severity Index (PDSI) for the 2.5 years prior to each focal drought](tables_figures/drought_plot.jpg){width=600px}

### 2019-11-04 manuscript/climate_sensitivity_draft.Rmd
created and added Fig. S2- drought plot

In the 60-year period between 1950 and 2009, there were three droughts that met our criteria of anomalously dry climatic conditions coupled with substantial reductions in tree growth for at least some portions of the community: 1966, 1977, and 1999 (Fig. 1). 
We excluded one year (1991) meeting the growth reduction criteria (26.5% of trees experienced >30% growth reduction, mean resistance= -13.8%) because this year was not among the driest in terms of May-August [PET-PRE] or PDSI (Table S3). Rather, the severity of growth reduction may be explained by defoliation by gypsy moths (*Lymantria dispar* L.) from approximately 1988-1995, which most stronly impacted *Quercus* spp. (*Cite Shenandoah paper, if accepted*). 
Climatically, these droughts included three of the five years between 1950 and 2009 with greatest moisture deficit (PET-PRE) during the peak growing season months of May-August, which are the months to which annual tree growth at this site is most sensitive [@helcoski_growing_2019]. Specifically, 1966, 1977, and 1999 had mean MJJA PET-PRE of 83.37, 86.97, and 80 mm mo<sup>-1</sup>, respectively. The years 1964 and 2007 also ranked in the top five driest (PET-PRE =83.87 and 82.13 mm mo<sup>-1</sup>), but were not among the lowest in terms of PDSI and were not identified as a pointer yeasr (Table S3)

>>>>

In the 60-year period between 1950 and 2009, there were three droughts that met our criteria of anomalously dry climatic conditions coupled with substantial reductions in tree growth for at least some portions of the community: 1966, 1977, and 1999 (Figs. 1, S2). 
We excluded one year (1991) meeting the growth reduction criteria (26.5% of trees experienced >30% growth reduction, mean resistance= -13.8%) because this year was not among the driest in terms of May-August [PET-PRE] or PDSI (Table S3). Rather, the severity of growth reduction may be explained by defoliation by gypsy moths (*Lymantria dispar* L.) from approximately 1988-1995, which most stronly impacted *Quercus* spp. (*Cite Shenandoah paper, if accepted*). 
Climatically, these droughts included three of the five years between 1950 and 2009 with greatest moisture deficit (PET-PRE) during the peak growing season months of May-August, which are the months to which annual tree growth at this site is most sensitive [@helcoski_growing_2019]. Specifically, 1966, 1977, and 1999 had mean MJJA PET-PRE of 83.37, 86.97, and 80 mm mo<sup>-1</sup>, respectively. The years 1964 and 2007 also ranked in the top five driest (PET-PRE =83.87 and 82.13 mm mo<sup>-1</sup>), but were not among the lowest in terms of PDSI and were not identified as a pointer yeasr (Table S3)
